GxHash: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities

### 2023-10-12 article/article.tex
Update readme

This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms, which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging from nanoseconds to microseconds. Given these considerations, the paper intentionally excludes Thread-Level Parallelism
(TLP) as a viable strategy for performance optimization.\\\\
Firstly, it's worth mentioning that TLP is orthogonal to the methods being explored in this paper.
TLP focuses on optimizing coarser-grained operations by distributing tasks across multiple threads, which doesn't directly align with the fine-grained performance improvements we aim to achieve.\\\\
Secondly, introducing TLP would necessitate the incorporation of task scheduling, synchronization, and context switching.
These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to leave it aside in this paper.

@@

@@

\subsection{The Wide-Pipe Construction Variant} \label{widepipe}

@@

>>>>

\subsubsection{Multithreading}

This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms, which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging from nanoseconds to microseconds. Given these consideration, the paper intentionally excludes Thread-Level Parallelism
(TLP) as a viable strategy for performance optimization.\\\\
Firstly, it's worth mentioning that TLP is orthogonal to the methods being explored in this paper.
TLP focuses on optimizing coarser-grained operations by distributing tasks across multiple threads, which doesn't directly align with the fine-grained performance improvements we aim to achieve.\\\\
Secondly, introducing TLP would necessitate the incorporation of task scheduling, synchronization, and context switching.
These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to leave it aside in this paper.

@@

Ensuring portability (algorithm generating the same hashes consistently accross different platforms for a given input) is a constrain that may hinder some potential optimization. Our goal being performance first, and our scope of application mainly focused on in-process usages such as hashtables, portability can be left out for these researches. Yet, it remains crutial for the algorithm to work under both x86 and ARM 64-bit platforms that represent most of today's general purpose computing systems.

@@

\clearpage
\subsection{The Wide-Pipe Construction Variant} \label{widepipe}

@@

An alternative to chaining usages of \( f \) is to compress lane hashes by pair, and subsequently compressing the resulting hashes also by pair until we are left with a single hash (for instance \(f(f(f(H_1, H_2), f(H_3, H_4)), f(...))\)). In practice, this would allow some form of ILP on the final hash composition as well, decreasing as we get closer to the final hash.
